\documentclass[11pt] {article}
\usepackage[letterpaper, margin=1in]{geometry}

\title{Dodgeball Tactics}
\author{Zach Stecher}
\date{Due: 9/13/16}

\begin{document}

\maketitle

\section*{Game Overview}
Dodgeball Tactics is a turn-based tactical game set in the gym of your neighborhood school. Two players match wits(and imaginary arms) head-to-head as they control their respective dodgeball team's positioning and strategy to eliminate the other team's players first. Above all, remember the 5 D's: Dodge, Dip, Duck, Dive and Dodge!

\section*{Target Audience}
Dodgeball Tactics is aimed at consumers ages 12+, with a focus on those who may already enjoy games that combine tactical thinking and planning with elements of random chance, such as Risk, Dungeons and Dragons, and Magic: The Gathering.

\section*{Platform}
Dodgeball Tactics is being developed as a board game with the intention of building and launching a PC version shortly after.

\section*{Features}
\begin{itemize}
\item Players take turns moving their team around a grid-based board set in the school gym where the yearly big dodgeball game is happening.
\item Player units eliminate opposing player units by hitting them with dodgeballs or catching dodgeballs thrown at them.
\item Dodgeball throws are determined to hit, miss or be caught based on a combination of distance from the target (in spaces) and a roll of dice, with modifiers depending on the involved units' types.
\item Each team has three different unit types. An offensive type, a defensive type, and one on each team being a 'hero' type unit known as the 'Ace'.
\item Players may bring eliminated units back into the game by catching a ball thrown by an opponent.
\item The first team to eliminate every unit on the opposing team is the winner!
\end{itemize}

\end{document}