\documentclass [12pt]{article}

\title{\small{\textbf{Design Document For:}}\\[1in]{\Huge{\textbf{Dodgeball: Eldritch Escape}}}}
\author{Zach Stecher}
\date{Due: 9/22/16}

\begin{document}

\maketitle
\newpage

\section*{Game Overview}

\subsection*{Introduction}

Eldritch Escape is a sidescrolling platformer where players play as Andy, the ace of his school's dodgeball team. Kidnapped by his school's biggest rival-Lovecraft High-right before the big game and stashed inside the basement of their school, the player must guide Andy through weirdness and insanity to escape Lovecraft High and make it back home in time for the game.

The game takes place just before Andy's school is set to take on Lovecraft High in the biggest dodgeball game of the year. Lovecraft High's team-The Horrors-decide to kidnap Andy to force  his team to forfeit, and tie him up in the basement of their school. The player must navigate a surreal school full of platforming elements, eldritch enemies, and traps to progress.

\subsection*{Targets}

Eldritch Escape is targeted towards players age 12+ who enjoy 2D platforming experiences. The game is targeted to launch on PC.

\subsection*{Design Goals}

The aim of Eldritch Escape is to provide a fun platforming experience that combines the comisc horror of the Lovecraftian vein of fiction with a lighthearted setting of a school to achieve a black comedy feel. The horror elements should double as both an indication of the threat to the player, as well as a source of comedic relief that the setting is treated as something normal. By layering these thematic elements on top of a fast-paced platformer we aim to create a memorable experience.

\section*{Feature Set}

\subsection*{General Features}

\begin{itemize}
\item Fast-paced 2D platforming
	\begin{itemize}
	\item Run, jump and fight your way out!
	\end{itemize}
\item Ranged combat by throwing dodgeballs
	\begin{itemize}
	\item It doesn't make any sense to them either! But play to your strengths right?!
	\end{itemize}
\item Fascinating eldritch level design
	\begin{itemize}
	\item Disgusting tentacles, portals to other dimensions, and a building layout that doesn't seem like it would be able to stand in a physical reality! Try not to go insane.
	\end{itemize}
\item Horrible, mutated enemies
	\begin{itemize}
	\item Battle grotesque students(just don't call them that to their faces) on your quest to escape the confines of your captors' school and make it back in time!
	\end{itemize}
\item Escape it all just so you can help your team win a dodgeball game (Your life is unimportant)
	\begin{itemize}
	\item Who says everyone has to save the world?
	\end{itemize}
\end{itemize}

\subsection*{Gameplay}

\begin{itemize}
\item Move Andy left and right, jump, and throw dodgeballs
\item Overcome obstacles by avoiding traps and pitfalls, eliminating enemies and solving puzzles
\item Defeat the spawn of the Old Gods by hitting them with dodgeballs
\end{itemize}

\section*{Game World}

\subsection*{Overview}

Andy is the ace of his local high school's dodgeball team. Their biggest rival has always been Lovecraft High, the elite school that only admits direct relatives of Cosmic Deities. Lovecraft high will do practically anything to get an edge over anyone that dares challenge their superiority. In the past they've broken into rival schools, stolen game-time equipment, driven coaches to frothing insanity... the usual things hyped up kids will do.

\subsection*{Game Location}

The game itself will take place inside Lovecraft High. Andy escapes his bonds after being kidnapped and begins in the basement of the school. The front door isn't so much locked as it is a portal to another dimension, so that won't work. The player must navigate Andy through different sections of the school-the basement, the science lab, the cafeteria, etc.-in order to find a way out back into his home dimension.

\subsection*{Travel}

The player moves through the game world in a 2D space by moving left or right, and jumping. The school is one large interconnected level populated by the students of Lovecraft High as well as objects like pushable boxes.
\newpage

\subsection*{Characters}

\begin{itemize}
\item Andy
	\begin{itemize}
	\item Ace of his school's dodgeball team. Kind and confident. Still gets picked on at school by the football players.
	\end{itemize}

\item Sandra
	\begin{itemize}
	\item Andy's girlfriend. Manager of the cheerleading club. Normally soft-spoken and nerdy, but incredibly forceful and loud when agitated.
	\end{itemize}

\item Kl'gnyth
	\begin{itemize}
	\item Captain of Lovecraft High's dodgeball team. Arrogant and incomprehensible. Kl'gnyth has a fierce personal rivalry with Andy, believing him to be the biggest threat to his dominance of both high school and the mortal world.
	\end{itemize}


\item Soggoth
	\begin{itemize}
	\item Andy's only ally inside Lovecraft High. Offers suggestions and tips from afar. Sarcastic and non-serious personality. Absolutely hates Kl'gnyth sa he believes he's stifling the chaotic freedom once enjoyed at the school in favor of tyrannical order.
	\end{itemize}
\end{itemize}

\subsection*{Level Design}

Because Lovecraft High is a school for the relatives of cosmic deities-beings of unfathomable will and power-the school itself is no ordinary high school. The halls and classrooms are infested with eldritch horrors from other dimensions. Tentacles and eyes grow out of the walls; mad whispers echo in the hallways; girl students pierce their ears and dye their hair and none of the teachers say anything. The atmosphere is dark with a log of purple, dark red and bright green coloring.

\subsection*{Basement}

The basement level serves as the first area of the game, doubling as a short tutorial. Players awaken in a room after being tied up, having already broken free from their bonds. The game quickly displays the controls to move left and right. After exiting this first room, the player is confronted with a crate. The game then displays the control for jump. After jumping up some inclining steps, the payer is confronted with their first enemy. This enemy is basic and acts as little more than practice for the player. The game then displays the "attack" control and how it works. The player defeats this enemy and moves forward. Here, the player is confronted with their first crate pushing puzzle, along with two enemies. At this point, they are contacted telepathically by Soggoth. After an introduction, Soggoth explains that the player is stuck in the basement and will have to escape past Kl'gnyth's mindslaved student followers. He suggests that you utilize objects around you to climb out, but warns that the student enemies will not let you push crates past them without doing something to stop you. The player solves this puzzle by eliminating the enemies and then pushing both sets of crates to the leftmost wall.

After climbing these crates, the player is presented with a more difficult puzzle to clear the level. The player must find a way to stack 4 boxes on top of each other so that they can reach the ledge above. After solving this puzzle, the player advances by defeating a few more enemies on their way to the ladder that leads them out of the basement and onto the next level.

\subsection*{1st Floor Halls}


\end{document}
